% LaTeX resume using res.cls
\documentclass[line, margin]{res}
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion
%\newcommand\textbox[1]{\parbox{.5\textwidth}{#1}}


% Center the name over the entire width of resume:
\name{Ayan Sengupta}

% address begins here

\address{\parbox{0.42\linewidth}{ Sir Peter Mansfield Imaging Center\\Dept. of Physics and Astronomy\\University of Nottingham\\United Kingdom\\Ayan.Sengupta@nottingham.ac.uk\\+44-7858789818}}
%\address{}
%\address{}
%\address{}

%\phone{}

\begin{document}
\begin{resume}
\section{Education}

\textbf{Ph.D. (Dr. rer. nat.), Psychoinformatics} \hfill 2013-2016\\ 
Otto-von-Guericke-Universit\"{a}t \hfill Germany\\
\small\textbf{Thesis:} \textit{The Effect of Acquisition Resolution and\\
Magnetic Field Strength on Multivariate Decoding of fMRI}

\textbf{M.S., Computer Science and Engineering} \hfill 2010-2012\\
University of Nebraska, Lincoln \hfill USA\\
\small\textbf{Thesis:} \textit{MRI and histo-pathological image co-registration\\ 
of brain for HIV-based murine model of neurocognitive decline}

\textbf{B.Tech., Electronics and Communication Engineering} \hfill 2004-2008\\
West Bengal University of Technology \hfill India\\



\section{Academic Honors}
\textbf{DFG Research Fellowship} \hfill 2013\\
Otto-von-Guericke-Universit\"{a}t \hfill Germany\\

\textbf{Graduate Teaching Assistantship} \hfill 2010\\
University of Nebraska, Lincoln \hfill USA\\

\textbf{Chancellor's Fellowship} \hfill 2010\\
University of Nebraska, Lincoln \hfill USA\\

\textbf{Oracle 9i PL/SQL Award of Achievement from Oracle University} \hfill 2010\\

\textbf{Sun Certified JAVA programmer (SCJP 1.5)} \hfill 2009\\

\textbf{National Merit Scholarship} \hfill 2002 and 2004\\
Exceptional academic performance in Middle and High School \hfill India\\



\section{Professional and Research Experience}

\textbf{Research Fellow} \hfill 2016-present\\
Sir Peter Mansfield Imaging Center\\
University of Nottingham \hfill UK\\
Supervisor: \href{https://www.nottingham.ac.uk/physics/people/susan.francis}{\textbf{Prof. Susan Francis}}, Dept. of Physics and Astronomy\\

\begin{itemize}
    \item Somatotopic mapping of digits in human primary somatosensory cortex. 
    \item Multivariate Analysis of BOLD response to Intraneural Microstimulation and vibrotactile stimulation
\end{itemize}
\newpage
\textbf{DFG Research Associate} \hfill 2013-2016\\
Otto-von-Guericke-Universit\"{a}t \hfill Germany\\
Supervisor: \href{http://mih.voxindeserto.de/}{\textbf{Dr. Michael Hanke}}, Dept. of Psychoinformatics, OVGU\\
Co. Supervisor: \href{http://www.ipsy.ovgu.de/ipsy/en/Departments/Experimental+Psychology/People.html}{\textbf{Dr. Stefan Pollmann}}, Dept. of Experimental Psychology, OVGU

\begin{itemize}
    \item Multivariate Pattern Analysis of ultra-high field (7T) multi-resolution fMRI for orientation decoding in human primary visual cortex. 
    \item Comparison of Magnetic Field Strength (3T vs 7T) for better SNR and sensitivity in multi-resolution fMRI, to find its contribution to orientation classification analysis.
\end{itemize}


\textbf{Technical Officer}, Govt. of India \hfill 2012-2013\\
National Brain Research Center \hfill India\\
Collaborator: \href{http://mcin-cnim.ca/people/alans-cv/}{\textbf{Dr. Alan Evans}}, MNI, McGill University 
\begin{itemize}

    \item Designed and implemented of the first Tele-Medicine grid of Neuroscience in India in collaboration with McGill University, Montreal. This project was an extension of \href{http://mcin-cnim.ca/neuroimagingtechnologies/loris/}{\textbf{LORIS}} platform for studying Dementia in the aging population in India. 
    \item Research on determining track followed by neural stem cells from sub-ventricular zone to the area of infarct during neurogenesis in stroke models of rodents. Worked on co-registration of MR angiography and DTI image volumes in this project.
    \item Worked on the field of Computational Neuroscience, designing and running fMRI experiments.
\end{itemize}



\textbf{Visiting Scholar} \hfill 2012\\
National Institute of Mental Health and Neurosciences \hfill India\\
Supervisor: \href{http://mbial.weebly.com/dr-john-p-john.html}{\textbf{Dr. John P. John}}, Dept. of Psychiatry, NIMHANS
\begin{itemize}
    \item Hands-on experience in Multi-modal Imaging like fMRI,MRS, EEG, High-Angular DTI
    \item Analysis and correlation of fMRI and DTI images
\end{itemize}



\textbf{Graduate Researcher and Teaching Assistant} \hfill 2010-2012\\
University of Nebraska Lincoln \hfill USA\\
Supervisor: \href{http://cse.unl.edu/~samal/}{\textbf{Dr. Ashok Samal}}, Dept. of Computer Science, UNL\\
Co. Supervisor: \href{http://www.unmc.edu/radiology/faculty/liu.html}{\textbf{Dr. Yutong Liu}}, Dept. of Radiology, UNMC

\begin{itemize}
    \item Worked in collaboration with University of Nebraska Medical Center, USA on a project involving automatic landmark selection and optimization of landmarks, for non-linear co-registration of MRI slices of rat brains with corresponding histological images. This project was done for tracking growth of HIV induced neuro-cognitive disorders in murine models.
    \item Taught 'Introduction to computer Science with Java' and was in-charge of 'Introduction to data structure and algorithms' laboratory
\end{itemize}


\textbf{Programmer Analyst} \hfill 2008-2010\\
Cognizant Technology Solutions \hfill India\\

\begin{itemize}
    \item Defect-resolving and performance-tuning of databases. Worked on design and development of Global Strategic Trading Platform of JP Morgan Chase Bank, USA
    \item Sybase Analyst and Developer, Java developer
\end{itemize}


\section{Technical Strengths}
\begin{itemize}
    \item Programming Languages: Python, MATLAB, BASH, C++, JAVA
    \item Neuroimaging Softwares: PyMVPA, FSL, Freesurfer, AFNI, SPM
\end{itemize}


\section{Conference Presentations}
\textbf{Presenter}
\begin{itemize}
    \item Ayan Sengupta, Renat Yakupov, Oliver Speck, Stefan Pollmann and Michael Hanke (2015). \textbf{Optimal Resolution and Filtering for Orientation Decoding in V1 at 7T}. Organization of Human Brain Mapping 2015.  Presentation delivered at the Organization of Human Brain Mapping 2015 meeting, Honolulu, Hawaii, June, 2015. 

    \item Ayan Sengupta, Cecile Madjar and Samir Das (2014). \href{https://github.com/aces/DICOM_anonymizer/blob/master/README.md}{\textbf{DicAT - DICOM Anonymization Tool}} Organization of Human Brain Mapping 2014. The software was conceived, developed and presented in collaboration with LORIS team of McGill University at the Organization of Human Brain Mapping Hackathon, Berlin, June, 2014.

    \item Ayan Sengupta, Michael D. Boska, Howard E. Gendelman, Ashok Samal and Yutong Liu (2012). \textbf{Automation of Landmark Selection for Rodent Brain MRI-Histology Registration using Thin-Plate Splines}. Nebraska Annual Research Symposium 2012, Lincoln, Nebraska, 2012. 

 
\end{itemize}




\section{Publications}
\begin{itemize}
    \item \textbf{Ayan Sengupta}, Renat Yakupov, Oliver Speck, Stefan Pollmann and Michael Hanke. \textit{Ultra high-field (7Tesla) multi-resolution fMRI data for orientation decoding in visual cortex} (in press).\\
    \item \textbf{Ayan Sengupta}, Renat Yakupov, Oliver Speck, Stefan Pollmann and Michael Hanke. \href{http://www.sciencedirect.com/science/article/pii/S1053811916307625}{\textit{The effect of acquisition resolution on orientation decoding from V1 BOLD fMRI at 7 Tesla}}.\\
    \item \textbf{Ayan Sengupta}, Falko Kaule, J. Swaroop Guntupalli, Michael B. Hoffmann, Christian H\"{a}usler, J\"{o}rg Stadler and Michael Hanke. \href{http://www.nature.com/articles/sdata201693}{\textit{A studyforrest extension, retinotopic mapping and localization of higher visual areas}}.\\
    \item Michael Hanke,  Nico Adelh\"{o}fer, Daniel Kottke, Vittorio Iacovella, \textbf{Ayan Sengupta}, Falko R. Kaule, Roland Nigbur, Alexander Q. Waite, Florian Baumgartner and J\"{o}rg Stadler. \href{http://www.nature.com/articles/sdata201692}{\textit{A studyforrest extension, simultaneous fMRI and eye gaze recordings during prolonged natural stimulation}}.\\
	\item Samir Das, C\'{e}cile Madjar, \textbf{Ayan Sengupta}, Zia Mohades. \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5103253}{\textit{LORIS: DICOM anonymizer.}}\\
	\item \textbf{Ayan Sengupta}. \href{http://digitalcommons.unl.edu/computerscidiss/45/}{\textit{Automation of Landmark Selection for Rodent Brain MRI-Histology Registration using Thin-Plate Splines}}.\\
\end{itemize}




%~ \section{References}
%~ \begin{enumerate}
    %~ \item []\href{http://www.ipsy.ovgu.de/ipsy/en/Departments/Experimental+Psychology/People.html}{\textbf{Dr. Stefan Pollmann}}\\Professor, Department of Experimental Psychology\\Otto-von-Guericke-Universit\"{a}t\\Institut f\"{u}r Psychologie\\Building 24 R-008, Universit\"{a}tplatz 2\\39106, Magdeburg\\Email: stefan.pollmann@ovgu.de\\Phone: +493916718474

    %~ \item []\href{http://mih.voxindeserto.de/}{\textbf{Dr. Michael Hanke}}\\Junior Professor, Department of Psychoinformatics\\Otto-von-Guericke-Universit\"{a}t\\Institut f\"{u}r Psychologie\\Building 23 R-009, Universit\"{a}tplatz 2\\39106, Magdeburg\\Email: michael.hanke@ovgu.de\\Phone: +493916718481

    %~ \item []\href{http://mcin-cnim.ca/people/alans-cv/}{\textbf{Dr. Alan Evans}}\\Professor, Department of Neurology/Neurosurgery,\\Department of Biomedical Engineering, Medical Physics Unit\\Director, Montreal Consortium for Brain Imaging Research\\Co-Director, Ludmer Centre for Neuroinformatics and Mental Health\\Montreal Neurological Institute, McGill University\\3801, rue University\\Montréal, QC\\Canada H3A 2B4\\Email: alan@bic.mni.mcgill.ca
%~ \end{enumerate}

\end{resume}
\end{document}

